Capitalized Title Here

### 2021-03-04 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of comments

The automated framework  used in this paper was proposed by @aoas. In order to obtain bullet signatures from the x3p files of bullet land impressions, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr]. `x3ptools` \hh{is a package to read, write, and generally, process } x3p files. 
<!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).--> 
\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper). Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face. Engravings are scratch marks.}
\autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area. The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks. The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land impression. `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`). \autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression. `bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land impression in the middle is kept. With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature. \autoref{fig:process} illustrates this framework. Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors. Note that NIST researchers used a different way of getting the bullet signatures in their paper [@cmps].

>>>>

The automated framework  used in this paper was proposed by @aoas. In order to obtain bullet signatures from the x3p files of bullet land impressions, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr]. `x3ptools` \hh{is a package to read, write, and generally, process } x3p files. 
<!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).--> 
\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper). Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face. Engravings are scratch marks.}
\autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area. The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks. The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land impression.
\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description. Could you instead describe things conceptually, and then link to the code that does this particular image?} `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal \hh{XXX ideal is a dangerous word} height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`). \autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression. `bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land impression in the middle is kept. With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature. \autoref{fig:process} illustrates this framework. Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors. Note that NIST researchers used a different way of getting the bullet signatures in their paper [@cmps].
